A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-30 paper/paper.tex
paper: fix some citations

In the context of typed functional programming, Reynolds' parametricity~\cite{} interprets types as relations characterizing the observational equality of programs of this type. Parametricity can be iterated and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{}. It has then be noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.

@@

\newpage
\begin{thebibliography}{10}
  \bibitem[Bez]{Bezem14}
  Bezem, M., Coquand, T., \& Huber, S. (2014, July). A model of type theory in cubical sets. \emph{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol. 26, pp. 107-128). Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.

>>>>

In the context of typed functional programming, Reynolds' parametricity~\cite{Reynolds72} interprets types as relations characterizing the observational equality of programs of this type. Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{Johann17,Altenkirch15,Moulin16}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{Bernardy12,Moulin16}. It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.

@@

\newpage
\begin{thebibliography}{10}
  \bibitem[Reynolds72]{Reynolds72}
  Reynolds, J. C. (1972, August). Definitional interpreters for higher-order programming languages. \emph{In Proceedings of the ACM annual conference-Volume 2} (pp. 717-740).

  \bibitem[Johann17]{Johann17}
  Johann, P., \& Sojakova, K. (2017). Cubical categories for higher-dimensional parametricity. \emph{arXiv preprint arXiv:1701.06244}.

  \bibitem[BernardyMoulin]{Bernardy12}
  Bernardy, J. P., \& Moulin, G. (2012, June). A computational interpretation of parametricity. \emph{In 2012 27th Annual IEEE Symposium on Logic in Computer Science} (pp. 135-144). IEEE.

  \bibitem[AltenkirchKaposi]{Altenkirch15}
  Altenkirch, Thorsten, and Ambrus Kaposi. "A nominal syntax for internal parametricity." \emph{TYPES 2015} (2015): 21.

  \bibitem[Moulin16]{Moulin16}
  Moulin, G. (2016). \emph{Internalizing parametricity.} Department of Computer Science and Engineering, Chalmers University of Technology.

  \bibitem[Bez]{Bezem14}
  Bezem, M., Coquand, T., \& Huber, S. (2014, July). A model of type theory in cubical sets. \emph{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol. 26, pp. 107-128). Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.
